\tldatecventry{2023}{STAT 151}{Introduction to Statistical Computing}{University of Nebraska - Lincoln}{Flipped synchronous. Evals: 4.55 (mean), 5 (median)}{}
\tldatecventry{2023}{STAT 251}{Data Wrangling}{University of Nebraska - Lincoln}{Flipped synchronous. Evals: 4.30 (mean), 5 (median)}{}
\tldatecventry{2023}{STAT 850}{Computing Tools for Statisticians}{University of Nebraska - Lincoln}{Flipped synchronous}{}
\tldatecventry{2023}{STAT 892}{Writing in Statistics/TA Prep}{University of Nebraska - Lincoln}{In person synchronous}{}
\tldatecventry{2022}{STAT 151}{Introduction to Statistical Computing}{University of Nebraska - Lincoln}{Flipped synchronous. Evals: 4.95 (mean), 5 (median)}{}
\tldatecventry{2022}{STAT 218}{Introduction to Statistics}{University of Nebraska - Lincoln}{Online asynchronous. Evals: 3.72 (mean), 4 (median)}{}
\tldatecventry{2022}{STAT 850}{Computing Tools for Statisticians}{University of Nebraska - Lincoln}{Flipped synchronous. Evals: 4.33 (mean), 5 (median)}{}
\tldatecventry{2022}{STAT 892}{Writing in Statistics/TA Prep}{University of Nebraska - Lincoln}{In person synchronous. Evals: 4.29 (mean), 5 (median)}{}
\tldatecventry{2022}{STAT 982}{Advanced Inference}{University of Nebraska - Lincoln}{Co-taught with Bertrand Clarke. Evals: 4.34 (mean), 5 (median)}{}
\tldatecventry{2021}{STAT 218}{Introduction to Statistics}{University of Nebraska - Lincoln}{Online asynchronous.. Evals: 4.01 (mean), 4 (median)}{}
\tldatecventry{2021}{STAT 850}{Computing Tools for Statisticians}{University of Nebraska - Lincoln}{Hybrid, flipped, synchronous. Evals: 4.79 (mean), 5 (median)}{}
\tldatecventry{2020}{STAT 218}{Introduction to Statistics}{University of Nebraska - Lincoln}{Initially in person synchronous, then online asynchronous. Evals: 4.20 (mean), 4 (median)}{}
\tldatecventry{2020}{STAT 850}{Computing Tools for Statisticians}{University of Nebraska - Lincoln}{Hybrid, flipped, synchronous. Evals: 4.76 (mean), 5 (median)}{}
\tldatecventry{2019}{STAT 585}{Data Technologies for Statistical Analysis}{Iowa State}{Co-taught with Heike Hofmann. Evals: 4.92 (mean), 5 (median)}{}
