\documentclass[11pt, letterpaper, sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}    % Width of the entire CV
\setlength{\hintscolumnwidth}{1.5in} % Width of the timeline on your left
\usepackage{pdfpages}
\usepackage{moderntimeline}
\usepackage{xpatch}
\usepackage{color, graphicx}
\usepackage[unicode]{hyperref}
\usepackage{xcolor}
\definecolor{link}{HTML}{295686}
\hypersetup{colorlinks, breaklinks,
            linkcolor=link,
            urlcolor=link,
            citecolor=link}
\usepackage{varwidth}
\usepackage[normalem]{ulem}
\usepackage{hyperref}

\usepackage{doi}% suppose to force DOI as verbatim

\clubpenalty=500
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands
\input{tweaks.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bib Info
 
\addbibresource{\jobname.bib} 

\intronote{donohoresponse}{Submitted as an invited response to Donoho's ``50 years of Data Science"}
% \DeclareFieldFormat{date}{\textbf{#1}}
% \renewbibmacro*{date}{\printtext[date]{\printdate}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Personal Information/Other Options
\tlmaxdates{2008}{2026}              % Beginning and start of your timeline

% Personal Information
\name{Susan}{Vanderplas}
\title{\emph{Curriculum Vitae}}
\address{349a Hardin Hall North Wing}{3310 Holdrege Street}{Lincoln, NE 68483-0961}
\phone[office]{402-472-7290}
% \phone[mobile]{515-509-6613}
%\phone[fixed]{+55~(11)~3091~2722}
\email{susan.vanderplas@unl.edu}
% \email{srvanderplas@gmail.com}                % optional, remove / comment the line if not wanted
% \email{srvander@iastate.edu}                % optional, remove / comment the line if not wanted
% \homepage{srvanderplas.com}                   % optional, remove / comment the line if not wanted
%\social[linkedin]{}                          % optional, remove / comment the line if not wanted
%\social[twitter]{srvanderplas}               % optional, remove / comment the line if not wanted
\social[github]{srvanderplas}                 % optional, remove / comment the line if not wanted
%\extrainfo{\emailsymbol \emaillink{}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makecvtitle
\vspace{-1cm}
\section{Education}
\tldatecventry{2015}{PhD}{Statistics}{Iowa State University}{}{Dissertation: The Perception of Statistical Graphics}
\tldatecventry{2011}{MS}{Statistics}{Iowa State University}{}{}
\tldatecventry{2009}{BS}{Psychology \& Applied Mathematical Sciences}{Texas A\&M University}{}{}
\medskip

\section{Professional Experience}

\tlcventry{2020}{0}{Assistant Professor}{Statistics Department}{}{University of Nebraska, Lincoln}{}%
\tlcventry{2018/2}{2019}{Research Assistant Professor}{Center for Statistics and Applications in Forensic Evidence}{}{Iowa State University}{}%
% \begin{itemize}
% \item Developed an analysis pipeline to process thousands of shoeprint images, in order to identify important features, examine wear over time, and assess methods for automatic identification of shoeprint matches.
% \item Developed software to automate uploads of bullet scans to NIST databases
% \item Supervised creation of a convolutional neural net for identification of class characteristics on shoe soles.
% \item Facilitated creation of a database front-end to provide access to longitudinal shoe outsole image data. \end{itemize}
% }

\tlcventry{2018/2}{2019}{Statistical Consultant}{Nebraska Public Power District}{}{}{Provided individual mentoring and project leadership to continue the Business Intelligence Embedded Agent program and provide support for R-related projects.}

\tlcventry{2015/6}{2018/2}{Statistical Analyst}{Nebraska Public Power District}{}{}{
%Conduct statistical analyses to improve NPPD's data-driven decision making (safety, profitability, and equipment reliability). Design and implement a program to train employees in statistical programming, data analysis, data visualization, and basic statistical modeling.
}%
% \begin{itemize}
% \item Worked with IT and Strategic Management to develop a plan for analytics/data science maturity at NPPD.
% \item Designed a mentoring program to train individuals as embedded data scientists to increase the ability of NPPD to effectively utilize data.
% \item Modeled employee turnover to identify individuals likely to retire or resign.
% \item Established automated statistical monitoring of plant conditions, department turnover, and human performance errors.
% \item Predicted likely direction of tornadoes based on location and topological factors to establish the risk of tornado guided missle debris damaging critical equipment.
% \item Evaluated the risk of climate fluctuations on operational readiness.
% \item Identified site conditions statistically associated with water accumulation in radiation detectors at a nuclear plant.
% \item Improved engineering margin in thermal limits management in a nuclear reactor core.
% \end{itemize}
% }

\tllabelcventry{2015/4}{2015/10}{2015}{Postdoc}{Iowa State University Office of the Vice President for Research}{}{}{
%Evaluate the relationship between faculty start-up packages and future productivity.
}%
% \begin{itemize}
% \item Evaluated faculty funding start-up packages to explore links between start-up funding and future productivity.
% \item Explored natural variation and underlying trends in grant receipts across Iowa State over a 20 year period.
% \end{itemize}
% }

% \tlcventry{2014}{2019}{Consultant}{}{}{}{Develop web applications, interactive data displays, and statistical analyses for clients including the Iowa Soybean Association, ISU Agronomy Labs, and the USDA.%\newline\href{https://www.iasoybeans.com/news/articles/online-risk-calculator-helps-farmers-estimate-late-season-nitrogen-deficiency/}{Nitrogen Deficiency in Corn}, \href{https://crops.extension.iastate.edu/facts/}{Crop Yield Forecast}
% }

% \bigskip
% \section{Research Interests}
% \hspace*{\hintscolumnwidth}%
% \hspace*{.8em}
% \begin{varwidth}[t]{.45\maincolumnwidth}
% \textcolor{color1}{\textbf{\footaddendumsize{COMPUTING \& GRAPHICS}}}
%     \begin{itemize}
%     \item Visual inference
%     \item Perception of charts
%     \item Interactive graphics
%     \item Image analysis
%     \item Computer vision 
%     \item Machine learning
%     \end{itemize}
% \end{varwidth}
% \hfill\begin{varwidth}[t]{.55\maincolumnwidth}
% \textcolor{color1}{\textbf{\footaddendumsize{FORENSICS}}}
%     \begin{itemize}
%     \item Statistical graphics in legal settings
%     \item Algorithmic mimicry of human perception
%     \item Automatic footwear identification
%     \item Firearms/toolmark analysis
%     \end{itemize}
% \end{varwidth}
% \clearpage

\section{Scholarship}
% \subsection{Publications}
\cvitem{}{\footnotesize Contribution percentages estimated from git contributions using \texttt{git fame} where possible. Not all projects have github repositories for which this is meaningful.}
\nocite{*}
\printbibliography[heading=subbibliography,keyword=pr,title={Journal Publications}]
\smallskip
\printbibliography[heading=subbibliography,keyword=npr,resetnumbers=true,title={Other Publications}]
\medskip
% \bibliographystyle{myplainyr}
% \bibliography{publications}
\cvitem{In Progress}{
    \begin{description}
    \item [Perception of Log Scales] Assessment of perception and use of log scales to display exponential growth. Data collection stage.
    \item [A Convolutional Neural Network for Outsole Recognition] Use CNNs to automate identification of class characteristics in images of footwear outsoles. Revision stage.
    % \item [Truthiness and Statistical Charts] Evaluate whether the truthiness effect (increased belief in a statement based on the presence of an accompanying picture) holds for statistical charts and maps. 
    % \item [Longitudinal Shoe Database] Design a database for sharing longitudinal shoe wear data, including powder prints, 2D scans, 3D scans, pictures, and crime-scene style casts and prints. Submitted to Forensic Science International, Oct 2020.
    \item [Bullet Signature Resampling] Method for resampling bullet signatures used to calculate match and non-match score distributions.% \href{https://github.com/srvanderplas/bulletsamplr}{Link to project}
    \end{description}
    }

\subsection{Grants}
\tlcventry{2021}{2022}{NIJ R\&D in Forensic Science}{Automatic Acquisition and Identification of Footwear Class Characteristics}{PI}{Funded, \$380,650 total}{}
\tlcventry{2020}{2025}{NIST}{Center for Statistics and Applications in Forensic Evidence}{PI}{Funded (\$20 million total, \$456,930 sub-award)}{}
\tlcventry{2020}{2023}{USDA CIGOFF}{Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation}{PI}{Funded (\$4,000,000 total, ~\$400,000 UNL subcontract split between 3 UNL PIs)}{}
\tlcventry{2021}{2022}{USDA NIFA AFRI}{Corn Residue Adaptive Grazing Strategies}{Collaborator}{Funded, \$300,000}{}
\tldatecventry{2020}{USDA NIFA AFRI}{Practical Framework to Facilitate Adoption of In-Season N Management Technology in Commercial Fields}{Collaborator}{Not funded, \$300,000}{}
\tldatecventry{2020}{NSF}{AI Institute: AgroAI: The Institute for Advancing Agriculture and Food in a Changing World Using AI}{Collaborator}{Not Funded, Total grant \$20 million, UNL subcontract request \$3,555,327}{}
% \tlcventry{2020}{2021}{NIJ R\&D in Forensic Science}{Automatic Acquisition and Identification of Footwear Class Characteristics}{PI}{Funded for 2020-2021 (\$386,984 total); paused during transfer to UNL}{}
\tlcventry{2020}{2023}{NSF}{Overcoming the Rural Data Deficit to Improve Quality of Life and Community Services in Smart \& Connected Small Communities}{PI}{Funded (\$1,500,000 total, \$123,445 subcontract)}{}
\tldatecventry{2019}{USDA AFRI-SAS}{A Cyber-Physical System for Data-Intensive Farm Management}{PI}{Not funded, \$3,000,000 total}{}
% \tlcventry{2019}{2021}{USDA National Institute of Food and Agriculture}{Understanding Opioid Risks in Rural and Micropolitan Communities: Economic Restructuring, Social Disorganization, and Local Responses.}{PI}{Award number: 2018-68006-27640. Funded for FY 2018-2021, \$498,401.00}{}
\tldatecventry{2019}{NIJ R\&D in Forensic Science}{Statistical Infrastructure for the Use of Error Rate Studies in the Interpretation of Forensic Evidence}{Collaborator}{Funded for FY 2019, \$197,699 total, \$57,596 ISU sub-award}{}
\tldatecventry{2018}{NIJ R\&D in Forensic Science}{Passive Acquisition of Footwear Class Characteristics in Local Populations}{PI}{Not funded, \$383,104}{}
\tldatecventry{2018}{NIJ R\&D in Forensic Science}{Evaluating Photogrammetry for 3D Footwear Impression Recovery}{PI}{Not funded, \$281,755}{}
\medskip
\subsection{Invited Talks}
\tldatecventry{2021}{How do you define a circle? Perception and Computer Vision Diagnostics}{JSM}{Section on Statistical Graphics}{Seattle, WA}{}
\tldatecventry{2020}{\sout{Do You See What I See? Leveraging Human Perception in Computer Vision Tasks.}}{JSM}{Section on Statistical Graphics}{Online, Session Cancelled due to COVID-related issues.}{}
\tldatecventry{2020}{Perception and Visual Communication in a Global Pandemic}{Data Science, Statistics, and Visualization}{SAMSI}{Online}{}
\tldatecventry{2020}{One of these things is not like the others: Visual Statistics and Testing in Statistical Graphics}{Data Science Symposium}{South Dakota State University}{Brookings, SD}{}
\tldatecventry{2020}{Big Data, Big Experiments, and Big Problems}{}{Plant and Animal Genome}{San Diego, CA}{}
\tldatecventry{2019}{Statistical Lineups for Bayesians}{JSM}{Section on Statistical Graphics}{Denver, CO}{}
\tldatecventry{2018}{Clusters Beat Trend!? Testing Feature Hierarchy in Statistical Graphics}{SDSS}{}{Reston, VA}{}
\tldatecventry{2015}{Animint: Interactive Web-Based Animations Using Ggplot2's Grammar of Graphics}{JSM}{}{Seattle, WA}{}
\tldatecventry{2014}{The curse of three dimensions: Why your brain is lying to you}{JSM}{Section on Statistical Graphics Student Paper Session}{Boston, MA}{}
\medskip
% \clearpage
\subsection{Contributed Talks}
\tldatecventry{2021}{Welcome to Forensic Statistics}{Data Mishaps Night}{}{Online}{}

\tldatecventry{2018}{Framed! Reproducing 150 year old charts}{JSM}{}{Vancouver, BC}{}

\tldatecventry{2017}{A Bayesian Approach to Visual Inference}{JSM}{}{Baltimore, MD}{}

\tldatecventry{2016}{Clusters Beat Trend!? Testing Feature Hierarchy in Statistical Graphics}{JSM}{}{Chicago, IL}{}

\tldatecventry{2015}{Visual Aptitude and Statistical Graphics}{InfoVis}{}{Chicago, IL}{}
\tldatecventry{2015}{Animint: Interactive, Web-Ready Graphics with R}{Great Plains R User Group}{}{Sioux Center, IA}{}

\tldatecventry{2014}{Do You See What I See? Using Shiny for User Testing}{JSM}{}{Boston, MA}{}

\tldatecventry{2013}{Signs of the Sine Illusion -- why we need to care}{JSM}{}{Montreal, ON}{}
\medskip

\subsection{Internal Talks}
\tldatecventry{2021}{Visual Statistics: Communication and Graphical Testing}{Animal Science Seminar}{}{}{}
\tldatecventry{2021}{How to Make Good Charts}{Biological and Systems Engineering GSA}{}{}{}
\tldatecventry{2020}{Statistical Evaluation of Firearms and Toolmark Evidence}{Statistics Department Seminar}{}{}{}

\subsection{Software}
\cvitem{}{\footnotesize Dates show initial involvement; only packages which are no longer maintained have end dates.}
% \tlcventry{2019}{0}{\texttt{LegoR}}{Acquisition of data about lego packages from Brickfinder, Lego.com, and Rebrickable}{}{}{}
\tldatecventry{2020}{\texttt{vinference}}{Analysis of visual inference experiments}{}{}{}
\tldatecventry{2019}{\texttt{ShoeScrubR}}{Cleaning shoe print data for future statistical analysis}{}{}{}
\tldatecventry{2019}{\texttt{groovefinder}}{Identification of grooves in scans of bullet land engraved areas}{}{}{}
\tldatecventry{2018}{\texttt{ShoeScrapeR}}{Acquisition of Shoe Images and Metadata from Online Retailers}{}{}{}
\tldatecventry{2018}{\texttt{bulletxtrctr}}{Automated matching of 3d bullet scans}{}{}{}
\tldatecventry{2018}{\texttt{x3ptools}}{Reading, manipulating, and visualizing x3p files}{}{}{}
\tldatecventry{2018}{\texttt{bulletsamplr}}{Resampling of bullet signatures}{}{}{}
\tldatecventry{2018}{\texttt{ImageAlignR}}{Image registration algorithms for forensics}{}{}{}
\tlcventry{2013}{2015}{\texttt{animint}}{animated, interactive web graphics for R using d3.js}{}{}{}

% \bigskip

% \section{Awards and Honors}
% \tldatecventry{2014}{ASA Section on Statistical Graphics}{Student Paper Award}{}{}{}
\clearpage
\section{Teaching}
\tldatecventry{2021}{Stat 218 - Introduction to Statistics (Online Async)}{University of Nebraska, Lincoln}{}{}{}
\tldatecventry{2020}{Stat 850 - Computing Tools for Statisticians}{University of Nebraska, Lincoln}{}{Course materials: https://srvanderplas.github.io/unl-stat850/}{}
\tldatecventry{2020}{Stat 218 - Introduction to Statistics}{University of Nebraska, Lincoln}{}{}{Mean evaluation: 4.2, Median: 4.0}
\tldatecventry{2019}{Stat 585 - Data Technologies for Statistical Analysis}{Iowa State University}{}{}{Co-taught, assisted with curriculum development. Mean evaluation: 4.92, Median: 5.0 }
\tlcventry{2017}{2018}{Business Intelligence Embedded Agent Program}{Nebraska Public Power District}{}{}{
Design and implement a program to mentor employees, providing instruction in data science and opportunities to apply new skills within the company. Lead one-on-one and group mentoring sessions to create a sense of community and reinforce skills learned through online courses. 16 students.
}
% \tldatecventry{2017}{R Workshop}{Nebraska Public Power District}{}{}{
% 3-day internal course on using R for data analysis. 10 students.
% }

\tlcventry{2013}{2014}{R Workshops}{Iowa State}{}{}{Introduction to R, ggplot2, data management and cleaning, package development, literate programming, and Shiny.}
%Designed and conducted workshops to teach R skills to the members of the university and local business community. Workshop topics included an introduction to R, ggplot2, data management with plyr, reshape2, and stringr, package development, document creation with knitr, linear models, and creating web applets with Shiny.}

% \tlcventry{2011}{2013}{Statistical Methods for Research}{Iowa State}{}{TA}{}%Stat 401}
%TA - Held office hours and graded labs and tests for Stat 401, a class composed primarily of graduate engineering students.}
% \vspace{-12pt}
% \tlcventry{2012}{2013}{Introduction to Business Statistics II}{Iowa State}{}{TA}{}%Stat 326}
%TA - Taught undergraduate business students statistical methods and use of JMP statistical software. Responsibilities included holding office hours and evening help sessions, developing lab materials, managing the course website on Blackboard, and grading labs, homework, and tests.}
% \vspace{-12pt}
% \tldatecventry{2012}{Introduction to Business Statistics II}{Iowa State}{}{TA}{}%Stat 326}
%TA - Taught undergraduate business students statistical methods and use of JMP statistical software. Responsibilities included holding office hours and evening help sessions, developing lab materials, managing the course website on Blackboard, and grading labs, homework, and tests.}
% \vspace{-12pt}
% \tldatecventry{2011}{Statistical Methods for Research}{Iowa State}{}{TA}{}%Stat 401}
%TA - Taught graduate social science students statistical methods and use of SAS statistical software. Responsibilities included teaching lab sessions, creating lab materials, holding office hours and grading homework and lab materials.}
% \vspace{-6pt}
% \tldatecventry{2011}{Empirical Methods for Computer Science}{Iowa State}{}{TA}{}%Stat 430}
% TA - Held office hours and graded homework for Stat 430, a class composed of graduate bioinformatics and computer science students.}

\section{Mentoring and Advising}
\subsection{Graduate Students}
\tldatecventry{2021}{Jayden Stack}{Statistics}{MS}{Automatic Recognition of Shoe Class Characteristics}{}
\tlcventry{2020}{2021}{Emily Robinson}{Statistics}{Ph.D}{Perception and Visual Inference}{Co-advised with Reka Howard}
\tlcventry{2020}{2021}{Denise Bradford}{Statistics}{Ph.D}{Data Science and Interactive Graphics}{}
\tldatecventry{2020}{Ved Piyush}{Statistics}{MS}{Machine Learning and Computer Vision}{}
\tlcventry{2019}{2021}{Joseph Zemmels}{Statistics}{MS, Ph.D}{Analysis and Matching of Cartridge Cases}{ Completed MS (Spring 2020). Co-advised with Heike Hofmann.}
\tlcventry{2019}{2020}{Eryn Blagg}{Statistics}{MS, Ph.D}{Analysis of Wear Development in Three-Dimensional Shoe Scans. }{Completed MS (Spring 2020). Co-advised with Heike Hofmann}
\tlcventry{2018}{2019}{Miranda Tilton}{Statistics}{MS}{Footwear Class Characteristics and Computer Vision. }{Completed MS (Spring 2019).}
% \tldatecventry{2019}{Charlotte Roiger}{Statistics}{MS}{}{Detection of Topological Features of Bullet Lands using Computer Vision. Estimated MS completion in Spring 2020. Co-advised with Heike Hofmann.}
\smallskip
\subsection{Undergraduate Students}
\tldatecventry{2021}{Xinyu Liu}{Actuarial Science and Computer Science}{UNL FYRE Program}{Machine learning for shoe sole images}{}
\tldatecventry{2019}{Jason Seo}{Computer Science and Statistics}{Undergraduate Research}{R package for visualization of neural networks using the python library keras-vis.}{}
% \tldatecventry{2019}{Jenny Ha}{Computer Science}{Undergraduate Research}{}{Database design for storing bullet scans and intermediate analysis products.}
\tlcventry{2018}{2019}{Talen Fisher}{Computer Engineering}{Undergraduate Research}{Tools for working with x3p files, database design for storing bullet scans and intermediate analysis products.}{}
\smallskip
\subsection{Summer Research Programs}
\tldatecventry{2019}{Molly McDermott and Andrew Maloney}{Research Experience for Undergraduates}{Summer 2019}{Bullet Scan Quality and Machine Learning}{}
\tldatecventry{2019}{Syema Ailia, Emmanuelle Hernandez Morales, Tiger Ji}{Research Experience for Undergraduates}{Summer 2019}{Rapid Quality Control Tools for Confocal Microscopy Scans}{}
\tldatecventry{2018}{Ben Wonderlin and Jenny Kim}{Young Engineers and Scientists}{Summer 2018}{Footwear Class Characteristics and Computer Vision}{}

\medskip
\section{Outreach}
\subsection{Forensic Practitioners}
\tldatecventry{2021}{Blog Post}{CSAFE}{}{Q\&A - Treatment of Inconclusive Results in Error Rates of Firearm Studies (\href{https://forensicstats.org/blog/2021/03/02/webinar-qa-treatment-of-inconclusive-results-in-error-rates-of-firearms-studies/}{Link})}{}
\tldatecventry{2021}{Webinar}{CSAFE}{}{Treatment of Inconclusive Results in Error Rates of Firearm Studies}{}
\tldatecventry{2020}{CSAFE Firearms Workshop}{}{}{Invited Talk: Open Source Software in Forensics}{}

\medskip
\section{Service}
\subsection{Service to the Discipline}
\tlcventry{2021}{2024}{Associate Editor}{Journal of Computational and Graphical Statistics}{}{}{}
\tlcventry{2020}{2023}{Associate Editor}{R Journal}{}{}{}
\tlcventry{2020}{2022}{Graphics Section Program Chair (2021)}{ASA}{Official duties include planning JSM sessions in 2020 and running the Data Expo in 2022}{}{}
\tldatecventry{2020}{Program Committee (Graphics)}{Symposium on Data Science and Statistics 2020}{Visualization Track co-chair}{}{}
\tlcventry{2019}{2021}{Gertrude Cox Scholarship Committee Member}{ASA}{}{}{Assisted with selection of the Gertrude Cox Scholarship recipients and honorable mentions}
\tldatecventry{2019}{Uncoast Unconference Organizing Committee}{}{Des Moines, IA}{}{Organized the first R Uncoast Unconference to bring R developers in flyover country together for a 3-day event. Over 50\% of the participants at the conference were women or minorities, and participants included students, academics, and industry R programmers with a variety of experience levels in R programming.}
\tlcventry{2017}{2019}{Graphics Section Representative to the Council of Sections}{ASA}{}{}{}

\subsection{Department and Institutional Service}
\tldatecventry{2021}{Data Science Joint Committee}{}{}{}{Committee of Math, Computer Science, and Statistics departments to develop a comprehensive undergraduate data science program.}
\tlcventry{2020}{2021}{Seminar Organizer}{}{}{}{Arrange speakers for the department seminar.}
\tldatecventry{2020}{SCIL 101 Poster Judge}{Fall Semester}{}{}{}
\tlcventry{2019}{2020}{Undergraduate Program Committee}{}{}{}{Design an undergraduate statistics major and submit the proposal to the university.}

\section{Training}
\tldatecventry{2020}{Summer Institute for Online Teaching}{}{}{}{Online course structure and backwards design principles}
% Reviews
% - JASA
% - JCGS
% - R journal
% - The American Statistician 
% - Springer (book)

% \section{Theses}
% \subsection{Dissertation}
% \cvitem{Title}{\emph{The Perception of Statistical Graphics}}
% \cvitem{Committee}{Dr.~Heike Hofmann (Chair), Dr.~Dianne Cook, Dr.~Sarah Nusser, Dr.~Max Morris, Dr.~Stephen Gilbert}
% \cvitem{Abstract}{\small Research on statistical graphics and visualization generally focuses
% on new types of graphics, new software to create graphics, interactivity, and usability
% studies. Our ability to interpret and use statistical graphics hinges on the interface between
% the graph itself and the brain that perceives and interprets it, and there is substantially less
% research on the interplay between graph, eye, brain, and mind than is sufficient to understand
% the nature of these relationships. This dissertation further explores the interplay between a static
% graph, the translation of that graph from paper to mental representation (the journey from
% eye to brain), and the mental processes that operate on that graph once it is transferred into
% memory (mind). Understanding the perception of statistical graphics will allow researchers
% to create more effective graphs which produce fewer distortions and viewer errors while reducing
% the cognitive load necessary to understand the information presented in the graph.
% }
% 
% \medskip
% 
% \subsection{MS Creative Component}
% \cvitem{Title}{\emph{Nonparametric statistical analysis of Atom Probe Tomography spectra}}
% \cvitem{Committee}{Dr.~Alyson Wilson (Chair), Dr.~Alicia Carriquiry, Dr.~Krishna Rajan}

\end{document}
